\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{// All comments are NOT created equal}

### 2015-05-17 paper/paper.tex
adding holes

\subsection{ROS \& Octomap}
For this research project we will make use of the Robot Operating System (ROS). ROS is a framework for creating robot software.  Within ROS, this project will use the octomap_server \cite{hornung13auro}.\\

The octomap_server works by loading a 3D map and distributing it to nodes in a compact binary format. Thus it can build and save 3D OctoMaps.\\

@@

Using this logic, the robot may run into issues because it does not have sensors above, below, or behind. This will not be covered in this paper but we will discuss this in \autoref{sec:limitations} and elaborate how it could be done in \autoref{sec:future}. Apart from running into objects, the robot can also fail to scan all areas due to the fact that we use the closest point in our field of vision to determine where we should be (see \autoref{fig:codeDistance}). In the case of spikes some areas may thus remain unscanned. The latter problem will be discussed in the next subsection.\\

\ednote{add octomap image}

>>>>

\subsection{ROS \& Octomap}
For this research project we will make use of the Robot Operating System (ROS). ROS is a framework for creating robot software.  Within ROS, this project will use the octomap\_server \cite{hornung13auro}.\\

The octomap\_server works by loading a 3D map and distributing it to nodes in a compact binary format. Thus it can build and save 3D OctoMaps.\\

@@

\begin{wrapfigure}{c}{\textwidth}
\vspace{-28pt}
  \begin{center}
  \fbox{
    \includegraphics[width=0.47 \textwidth]{assets/MapOnlyDistance}
    \includegraphics[width=0.4015 \textwidth]{assets/reefOriginalMappedComp}
    }
  \end{center}
\vspace{-20pt}
  \caption{Mapping using the Distance Algorithm}
  \label{fig:firstMapping}
\vspace{20pt}
\end{wrapfigure}

Overall this approach already provides us with good results as visible in \autoref{fig:firstMapping}. However, using this logic, the robot may run into issues because it does not have sensors above, below, or behind. This will not be covered in this paper but we will discuss this in \autoref{sec:limitations} and elaborate how it could be done in \autoref{sec:future}. Apart from running into objects, the robot can also fail to scan all areas due to the fact that we use the closest point in our field of vision to determine where we should be (see \autoref{fig:codeDistance}). In the case of spikes some areas may thus remain unscanned as can be seen in \autoref{fig:firstMappingProblems}. The latter problem will be discussed in the next subsection.\\

\begin{wrapfigure}{c}{\textwidth}
\vspace{-28pt}
  \begin{center}
  \fbox{
    \includegraphics[width=0.23 \textwidth]{assets/MapOnlyDistanceHole1}
    \includegraphics[width=0.23 \textwidth]{assets/MapOnlyDistanceHole2}
    \includegraphics[width=0.23 \textwidth]{assets/MapOnlyDistanceHole3}
    \includegraphics[width=0.23 \textwidth]{assets/MapOnlyDistanceHole4}
    }
  \end{center}
\vspace{-20pt}
  \caption{Mapping Problems using the Distance Algorithm}
  \label{fig:firstMappingProblems}
\vspace{20pt}
\end{wrapfigure}
